Using Machine Learning and Constraint Programming to Solve the Relational-To-Ontology Mapping Problem

### 2017-08-11 stp/paper_aaai/main.tex
integration graph

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=1.5,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1) {\scriptsize Event endDate};
	\node[data] (con) at (1,-1) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-1) {\scriptsize City.name};

@@

An example alignment graph is illustrated in Fig. \ref{FIG:ali}. Bigger 
examples 
can be found in \cite{Taheriyan2013}. Black links 
correspond to the links which are supported by the known semantic models. Blue 
and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones 
correspond to the ones added to connect Classes od the ontology that never 
appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

@@

	\node[class] (pe1) at (3,0)  {\small Person};
	\node[class] (co1) at (6,0) {\small Org.};
	\node[class] (ci1) at (1,0) {\small City};
	\node[class] (st1) at (-1,0) {\small State};

	\node[data] (pen) at (2.5,1) {\scriptsize Person.name};
	\node[data] (peb) at (4.3,1) {\scriptsize Person.birthDate};
	\node[data] (cin) at (1,1) {\scriptsize City.name};
	\node[data] (stn) at (-1,1) {\scriptsize State.name};
	\node[data] (con) at (6,1) {\scriptsize Org.name};

@@

	\node[class] (pl2) at (-1,0+\ysh)  {\small City};
	\node[class] (pe2) at (3,0+\ysh)  {\small Person};
	\node[class] (co2) at (1,0+\ysh) {\small Org.};
	\node[class] (ev2) at (6,0+\ysh) {\small Event};

	\node[data] (pen) at (2.5,-1+\ysh) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event endDate};
	\node[data] (con) at (1,-1+\ysh) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City.name};

@@

\end{tikzpicture}
\caption{Example of alignment graph.}
\label{FIG:ali}
\end{figure}

@@

An example of integration graph can be found in Fig. \ddg{TODO}.

>>>>

\usepackage{tikz}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=1.5,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

	\node[data] (pen) at (2.5,-1) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-1) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1) {\scriptsize Event.endDate};
	\node[data] (con) at (1,-1) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-1) {\scriptsize City.name};

@@

An example alignment graph is illustrated in Fig. \ref{FIG:ali}. Bigger 
examples 
can be found in \cite{Taheriyan2013}. Black links 
correspond to the links which are supported by the known semantic models. Blue 
and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones 
correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?} .

@@

	\node[class] (pe1) at (3,0)  {\small Person1};
	\node[class] (co1) at (6,0) {\small Org.1};
	\node[class] (ci1) at (1,0) {\small City1};
	\node[class] (st1) at (-1,0) {\small State};

	\node[data] (pen) at (2.3,1) {\scriptsize Person1.name};
	\node[data] (peb) at (4.2,1) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (0.7,1) {\scriptsize City1.name};
	\node[data] (stn) at (-1,1) {\scriptsize State.name};
	\node[data] (con) at (6,1) {\scriptsize Org1.name};

@@

	\node[class] (pl2) at (-1,0+\ysh)  {\small City2};
	\node[class] (pe2) at (3,0+\ysh)  {\small Person2};
	\node[class] (co2) at (1,0+\ysh) {\small Org.2};
	\node[class] (ev2) at (6,0+\ysh) {\small Event};

	\node[data] (pen) at (2.3,-1+\ysh) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-1+\ysh) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-1+\ysh) {\scriptsize Event.endDate};
	\node[data] (con) at (0.7,-1+\ysh) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-1+\ysh) {\scriptsize City2.name};

@@

\end{tikzpicture}
\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
{};}' and `\tikz{ \node[class,fill=orange!30!white] () at (0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\end{figure}

@@

An example of integration graph can be found in Fig. \ref{FIG:inte}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{Class 
	Nodes of Alignment Graph}};

	\node[data] (stn1) at (-3.9,-1) {\scriptsize S.n};
	\node[data] (cin1) at (-3.1,-1) {\scriptsize C1.n};
	\node[data] (pen1) at (-2.3,-1) {\scriptsize P1.n};
	\node[data] (peb1) at (-1.5,-1) {\scriptsize P1.b};
	\node[data] (con1) at (-0.7,-1) {\scriptsize O1.n};

	\path[draw,hasaA] (CLASS) edge[out=180,in=90] (stn1);
	\path[draw,hasaA] (CLASS) edge[out=190,in=90] (cin1);	
	\path[draw,hasaA] (CLASS) edge[out=200,in=90] (pen1);
	\path[draw,hasaA] (CLASS) edge[out=210,in=90] (peb1);	
	\path[draw,hasaA] (CLASS) edge[out=220,in=90] (con1);

% % % CC2
\def\ysh{0};

	\node[data] (cin2) at (0.7,-1+\ysh) {\scriptsize C2.n};
	\node[data] (con2) at (1.5,-1+\ysh) {\scriptsize O2.n};
	\node[data] (pen2) at (2.3,-1+\ysh) {\scriptsize P2.n};
	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E.s};
	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E.e};

	\path[draw,hasaA] (CLASS) edge[out=320,in=90] (cin2);	
	\path[draw,hasaA] (CLASS) edge[out=330,in=90] (con2);
	\path[draw,hasaA] (CLASS) edge[out=340,in=90] (pen2);
	\path[draw,hasaA] (CLASS) edge[out=350,in=90] (evs2);
	\path[draw,hasaA] (CLASS) edge[out=360,in=90] (eve2);

\node[rectangle, rounded corners,very thick,draw, dashed, 
brown!40!red!40!white,minimum 
height=18, minimum 
width=220] 
(source) at 
(0,-3) 
{};
\node[brown!40!red!40!white] 
(source) at 
(-4.1,-3) 
{$s^\star$:};
	\node[att] (a1) at (-3,-3) {\small Surame};
	\node[att] (a2) at (-1,-3) {\small Workplace};
	\node[att] (a3) at (1,-3) {\small Date};
	\node[att] (a4) at (3,-3) {\small Location};

	\path[draw] (a1) -- (stn1);
	\path[draw] (a1) -- (cin1);
	\path[draw] (a1) -- (pen1);
	\path[draw] (a1) -- (cin2);
	\path[draw] (a1) -- (pen2);

	\path[draw] (a2) -- (cin1);
	\path[draw] (a2) -- (con1);
	\path[draw] (a2) -- (con2);

	\path[draw] (a3) -- (peb1);
	\path[draw] (a3) -- (evs2);
	\path[draw] (a3) -- (eve2);

	\path[draw] (a4) -- (stn1);
	\path[draw] (a4) -- (cin1);
	\path[draw] (a4) -- (con1);
	\path[draw] (a4) -- (cin2);
	\path[draw] (a4) -- (con2);
\end{tikzpicture}
\caption{Example of integration graph. (`\tikz{ \node[att] () at (0,0)  
{};}' are attribute nodes). We omit weights for clarity. Data node labels are 
abbreviated but 
correspond to the ones shown in Fig \ref{FIG:ali}.}
\label{FIG:inte}
\end{figure}
